### 2013-02-16 doc/icml2013/evaluation.tex
edit

\begin{table*}[p]
\caption{Parameter Recovery Error $\|\theta^* - \hat \theta\|_F$ ($N = 500,000$).}
\label{tbl:parameter-recovery}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}

  \begin{tabular}{ r r r c c c }
\hline
\abovespace\belowspace
Variables ($b$) & Features ($D$) & Components ($K$) & Spectral & EM & Spectral + EM \\
\hline
\abovespace
%$\{1$, $ x_1$, $ x_1^4\}$ 
  1 & 4 & 2 & 1.52 $\pm$ 0.71 & 0.28 $\pm$ 0.82 & {\bf 0.13 $\pm$ 0.55} \\
%$\{1$, $ x_1$, $ x_2$, $ x_1^2 x_2^2\}$ 
  2 & 5 & 2 & 2.92 $\pm$ 1.10 & 0.00 $\pm$ 0.00 & {\bf 0.00 $\pm$ 0.00} \\
  2 & 5 & 3 & 3.76 $\pm$ 1.93 & 0.43 $\pm$ 1.07 & {\bf 0.23 $\pm$ 0.76} \\
%$\{1$, $ x_1$, $ x_2$, $ x_1 x_2^3$, $ x_1^2 x_2^2$, $ x_1^3 x_2 \}$ 
  2 & 6 & 2 & 4.52 $\pm$ 1.67 & 0.63 $\pm$ 1.29 & {\bf 0.18 $\pm$ 0.66} \\
\belowspace
  2 & 6 & 5 & 6.78 $\pm$ 2.18 & 2.29 $\pm$ 1.79 & {\bf 1.77 $\pm$ 1.89} \\

@@

\tableref{tbl:parameter-recovery} presents the Frobenius norm of the
difference between true and estimated parameters for the model, averaged
over 20 different random instances for each feature set and 10 attempts
for each instance. The experiments were run using $N = 500,000$ samples.

@@

\begin{figure}[th]
  \centering
  \includegraphics[width=0.50\textwidth]{figures/hist.pdf}
  \caption{Histogram over recovery errors between the three algorithms. $b = 1, d = 4, k = 3, N = 500,000$}
  \label{fig:hist}
\end{figure}

@@

\begin{figure*}[p]
  \centering
  \subfigure[Well Data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1833-decay.pdf}
  }
    \hspace{-2em}
  \subfigure[Misspecified Data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1-8-3-3-rm.pdf}
  }
  \caption{Recovery error vs $n$  ($b = 1, d = 5, K = 3, N = 500,000$).}
  \label{fig:vs-n}
\end{figure*}

@@

\begin{table*}[t]
\caption{Parameter Recovery Error $\|\theta^* - \hat \theta\|_F$ with misspecified data ($N = 500,000$).}
\label{tbl:parameter-recovery-mis}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}

  \begin{tabular}{ r r r c c c }
\hline
\abovespace\belowspace
Variables ($b$) & Features ($d$) & Components ($K$) & Spectral & EM & Spectral + EM \\
\hline
\abovespace
 1 & 4 & 2 &  2.94 $\pm$ 1.52 & 0.29 $\pm$ 0.85 &  {\bf 0.22 $\pm$ 0.72} \\
\belowspace
 2 & 5 & 3 &  3.82 $\pm$ 2.00 & 0.44 $\pm$ 1.12 &  {\bf 0.35 $\pm$ 1.00} \\
 2 & 6 & 5 &  9.89 $\pm$ 4.46 & {\bf 2.53 $\pm$ 1.77} &  2.69 $\pm$ 1.83 \\
 2 & 8 & 7 & 23.07 $\pm$ 7.10 & 9.62 $\pm$ 1.03 &  {\bf 8.16 $\pm$ 2.31}  \\
\hline

>>>>

\begin{table*}[p]
\caption{Parameter Recovery Error $\|\theta^* - \hat \theta\|_F$ ($n = 500,000$).}
\label{tbl:parameter-recovery}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}

  \begin{tabular}{ r r r c c c }
\hline
\abovespace\belowspace
Variables ($b$) & Features ($d$) & Components ($k$) & Spectral & EM & Spectral + EM \\
\hline
\abovespace
%$\{1$, $ x_1$, $ x_1^4\}$ 
  1 & 4 & 2 & 1.52 $\pm$ 0.71 & 0.28 $\pm$ 0.82 & {\bf 0.13 $\pm$ 0.55} \\
%$\{1$, $ x_1$, $ x_2$, $ x_1^2 x_2^2\}$ 
  2 & 5 & 2 & 2.92 $\pm$ 1.10 & 0.00 $\pm$ 0.00 & {\bf 0.00 $\pm$ 0.00} \\
  2 & 5 & 3 & 3.76 $\pm$ 1.93 & 0.43 $\pm$ 1.07 & {\bf 0.23 $\pm$ 0.76} \\
%$\{1$, $ x_1$, $ x_2$, $ x_1 x_2^3$, $ x_1^2 x_2^2$, $ x_1^3 x_2 \}$ 
  2 & 6 & 2 & 4.52 $\pm$ 1.67 & 0.63 $\pm$ 1.29 & {\bf 0.18 $\pm$ 0.66} \\
\belowspace
  2 & 6 & 5 & 6.78 $\pm$ 2.18 & 2.29 $\pm$ 1.79 & {\bf 1.77 $\pm$ 1.89} \\

@@

\tableref{tbl:parameter-recovery} presents the Frobenius norm of the
difference between true and estimated parameters for the model, averaged
over 20 different random instances for each feature set and 10 attempts
for each instance. The experiments were run using $n = 500,000$ samples.

@@

\begin{figure}[th]
  \centering
  \includegraphics[width=0.50\textwidth]{figures/hist.pdf}
  \caption{Histogram over recovery errors between the three algorithms. $b = 1, d = 4, k = 3, n = 500,000$}
  \label{fig:hist}
\end{figure}

@@

\begin{figure*}[p]
  \centering
  \subfigure[Well Data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1833-decay.pdf}
  }
    \hspace{-2em}
  \subfigure[Misspecified Data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1-8-3-3-rm.pdf}
  }
  \caption{Recovery error vs $n$  ($b = 1, d = 5, k = 3, n = 500,000$).}
  \label{fig:vs-n}
\end{figure*}

@@

\begin{table*}[t]
\caption{Parameter Recovery Error $\|\theta^* - \hat \theta\|_F$ with misspecified data ($n = 500,000$).}
\label{tbl:parameter-recovery-mis}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}

  \begin{tabular}{ r r r c c c }
\hline
\abovespace\belowspace
Variables ($b$) & Features ($d$) & Components ($k$) & Spectral & EM & Spectral + EM \\
\hline
\abovespace
 1 & 4 & 2 &  2.94 $\pm$ 1.52 & 0.29 $\pm$ 0.85 &  {\bf 0.22 $\pm$ 0.72} \\
\belowspace
 2 & 5 & 3 &  3.82 $\pm$ 2.00 & 0.44 $\pm$ 1.12 &  {\bf 0.35 $\pm$ 1.00} \\
 2 & 6 & 5 &  9.89 $\pm$ 4.46 & {\bf 2.53 $\pm$ 1.77} &  2.69 $\pm$ 1.83 \\
 2 & 8 & 7 & 23.07 $\pm$ 7.10 & 9.62 $\pm$ 1.03 &  {\bf 8.16 $\pm$ 2.31}  \\
\hline
